Manuscript plots

### 2023-11-15 manuscript_modelling_and_plots.Rmd
providing example fixation for Figure 4 alongside event-based summaries of entropy

This data contains every fixation for each participant for the automated driving periods. This is really only used for Figure 4 where the state spaces and fixations are described.

```{r}
# Setting digits to 15 mins that fixation duration s are not rounded to annoying precise. 
options(digits = 15)
fixations <- fread(file = here::here("ITS/Work package 6.5 (HiDrive)/TME study/Data/Eye data/fixations.csv"))
```

@@

```{r}
entropy.total <- fread(file = here::here("ITS/Work package 6.5 (HiDrive)/TME study/Data/Eye data/gaze entropy/Critical and Non-Critical/entropy.total.csv"))
```

>>>>

This dataframe contains an example fixation pattern for plotting Figure 4.

```{r}
# Setting digits to 15 mins that fixation duration s are not rounded to annoying precise. 
options(digits = 15)
example.fixation <- fread(file = here::here("gaze_entropy_heterogenous/data/example.fixation.csv"))
```

@@

```{r}
entropy.total <- fread(file = here::here("gaze_entropy_heterogenous/data/entropy.total.csv"))
```
